A comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-03-12 analysis/paper/paper.Rmd
update paper

```{r}
add_sfig(
  figure_file("score_aspects.svg", experiment_id="3-score_rules/5-score_aspects"), 
  "score_aspects", 
  "Different scores assess different aspects of the correspondence between a prediction and gold standard trajectory.",
  15, 
  8
)
```

@@

### Method execution
Each execution of a method on a dataset was performed in a separate task as part of a gridengine job. Each task was allocated one CPU core of an Intel(R) Xeon(R) CPU E5-2665 0 @ 2.40GHz, and was provided a maximum of 32GB in memory and 6 hours of wall time. One R session was started for each task, with the environment variable `R_MAX_NUM_DLLS` set to 500. The `base::set.seed` was overridden in order to prevent stochastic TI methods from pretending to be deterministic and/or robust. Timings of methods were measured for different steps along the executions, including preprocessing, postprocessing, each of the different metrics, and the method itself.

>>>>

```{r}
add_sfig(
  figure_file("score_aspects_v1.svg", experiment_id="3-score_rules/5-score_aspects"), 
  "score_aspects", 
  "Different scores assess different aspects of the correspondence between a prediction and gold standard trajectory.",
  15, 
  8
)
```

@@

### Method execution
Each execution of a method on a dataset was performed in a separate task as part of a gridengine job. Each task was allocated one CPU core of an Intel(R) Xeon(R) CPU E5-2665 @ 2.40GHz, and was provided a maximum of 32GB in memory and 6 hours of wall time. One R session was started for each task, with the environment variable `R_MAX_NUM_DLLS` set to 500. The `base::set.seed` was overridden in order to prevent stochastic TI methods from pretending to be deterministic and/or robust. Timings of methods were measured for different steps along the executions, including preprocessing, postprocessing, each of the different metrics, and the method itself.
